### 2020-04-30 final_report/methodology.tex
Vectorised sin toy model figure.
.fig file for sin toy model, some figure placement adjustments.

@@

Adaptive sampling techniques are widespread in the literature and have been
specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
Algorithm" achieved notable success by incorporating surrogate quality and
crowding distance scoring to identify optimal new samples, but was only tested
on a single-parameter domain. We theorised that a nondeterministic sample
generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
fare better for high-dimensional models by more thoroughly exploring all local
optima in the feature space. MCMC produces a progressive chain of sample points,
each drawn according to the same symmetric proposal distribution
from the prior point. These sample points will converge to a desired posterior
distribution, so long as the acceptance probability for these draws has a
particular functional dependence on that posterior value (see \cite{Zhou2018}
for a review).

%\footnote{An
%adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
%distribution to fit the posterior, was also implemented but not fully tested.}

\begin{wrapfigure}[22]{r}{0.55\textwidth}
	\centering
	\vspace{-5ex}
	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
	\caption{Schematic of QASS algorithm}
	\label{fig:qassplan}
\end{wrapfigure}

>>>>

\begin{wrapfigure}[25]{r}{0.55\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=0.7\textwidth]{fig4_qassplan.png}
	\caption{Schematic of QASS algorithm}
	\label{fig:qassplan}
\end{wrapfigure}

@@

Adaptive sampling techniques appear frequently in the literature and have been
specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling
Algorithm" achieved notable success by incorporating surrogate quality and
crowding distance scoring to identify optimal new samples, but was only tested
on a single-parameter domain. We theorised that a nondeterministic sample
generation approach, built around Markov Chain Monte Carlo methods (MCMC), would
fare better for high-dimensional models by more thoroughly exploring all local
optima in the feature space. MCMC produces a progressive chain of sample points,
each drawn according to the same symmetric proposal distribution\footnote{An
adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal
distribution to fit the posterior, was also implemented but not fully tested.}
from the prior point. These sample points will converge to a desired posterior
distribution, so long as the acceptance probability for these draws has a
particular functional dependence on that posterior value (see \cite{Zhou2018}
for a review).
